Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-18 writeup/rocha_etal.tex
Starts drafting SWOT relavant paragraph

% now SWOT

>>>>

% now SWOT
The upcoming Surface and Water Ocean Topography (SWOT) mission will measure
sea-surface height (SSH) on global scale with resolution of about 20 km, nearly
ten time higher than current nadir-looking altimeters. Thus the study of the
partition between geostrophic and ageostrophic flows across the submesoscales and
the quantification of their seasonality seasonality has an important application
to planning of the SWOT
mission. In particular, the presence of inertia-gravity waves may be consider
noise if one wants to diagnose surface currents from SSH.
